---
title: "macmod_processing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(raster)
library(tidyverse)
library(sf)
library(here)
library(ncdf4)
library(curl)
library(stars)

rasterOptions(maxmemory = 1e10,
              progress = "text")
```

## This is a script that crops/masks all data layers to our region of interest (W. Florida gulf), and also resamples all rasters to a 5 km grid.


### SABGOM
Let's start by exploring the SABGOM model output, and making a few base rasters/shapefiles around this.

```{r}
## sabgom <- raster(here("raw_data", "CMS_SABGOM_Model_Simulations_1510", "data", "sabgom_output_2005_rho.nc4"))

# Load in the sabgom data as a ncin file...
sabgom_ncin <- nc_open(here("raw_data", "CMS_SABGOM_Model_Simulations_1510", "data", "sabgom_output_2005_rho.nc4"))

# Pull a list of the variable names, keeping only the ones we want
# This keeps DIC, DIN, and SST, along with Lat and Lon
names <- names(sabgom_ncin$var[c(2, 3, 5, 6, 7)])

# Pull all the values of lat/long as a list
lon <- ncvar_get(ncin, "lon_rho")
lat <- ncvar_get(ncin, "lat_rho")

# Get the extent of the Sabgom models, using min/max lat lon from the above list
sabgom_extent <- extent(min(lon),
                        max(lon),
                        min(lat),
                        max(lat))

# Then we can view a ton of attributes about this data
# print(sabgom_ncin)
# view(sabgom)

# List all the file names we want to process.
files <- list.files(here("raw_data", "CMS_SABGOM_Model_Simulations_1510", "data"), pattern = "*rho.nc4", full.names = TRUE)
  
# Let's create an area of interest for the West Florida domain...this is estimated, not from the model (I can't find it?)
  wf_extent <- extent(-91, -80.5, 23, 38)
  # plot(wf_extent)

# start a function that will crop all these files
crop_fx <- function(input_files){
  # Open the input file...
  ncin <- nc_open(input_files)
  # We keep DIN, DIC, SST
  var_list <- names(ncin$var[c(2,3,5)])
  # We'll make a brick (and crop) function that we can apply to each variable
  # Our dimensions are lat long, and time is the z dimension.
  brick_fx <- function(variable){
    brk <- brick(input_files, varname = variable)
    # Change the extent of the brick to lat/lon
    extent(brk) <- sabgom_extent
    # Crop to west florida:
    cropped <- crop(brk, wf_extent)
    # Save the file
    writeRaster(cropped, 
                filename = here("output",
                                paste0(tools::file_path_sans_ext(basename(input_files)),
                                      "_",
                                      variable,
                                      ".tif")
                                ),
                overwrite = TRUE)
  }
  # run our function for each variable...
  lapply(var_list, brick_fx)
}

# Run the function for each file.
lapply(files, crop_fx)
```

```{r}
# Make a template raster...
test <- brick(here("output", "sabgom_output_2005_rho_DIC.tif"))
# 
# plot(test)
# 
# res(test)

blank <- raster(ext = extent(test), resolution = res(test))
writeRaster(blank, here("output", "base_raster_FL.tif"))

plot(blank, col = black)
```


## PAR from MODIS

These are OpenDAP links generated through the web browser for monthly averages.
First, we download the data...

```{r}
par_list <- c(
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20050012005031.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20050322005059.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20050602005090.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20050912005120.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20051212005151.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20051522005181.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20051822005212.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20052132005243.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20052442005273.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20052742005304.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20053052005334.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20053352005365.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20060012006031.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20060322006059.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20060602006090.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20060912006120.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20061212006151.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20061522006181.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20061822006212.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20062132006243.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20062442006273.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20062742006304.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20063052006334.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20063352006365.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20070012007031.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20070322007059.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20070602007090.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20070912007120.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20071212007151.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20071522007181.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20071822007212.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20072132007243.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20072442007273.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20072742007304.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20073052007334.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20073352007365.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20080012008031.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20080322008060.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20080612008091.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20080922008121.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20081222008152.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20081532008182.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20081832008213.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20082142008244.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20082452008274.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20082752008305.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20083062008335.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20083362008366.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20090012009031.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20090322009059.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20090602009090.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20090912009120.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20091212009151.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20091522009181.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20091822009212.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20092132009243.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20092442009273.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20092742009304.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20093052009334.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20093352009365.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20100012010031.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20100322010059.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20100602010090.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20100912010120.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20101212010151.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20101522010181.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20101822010212.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20102132010243.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20102442010273.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20102742010304.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20103052010334.L3b_MO_PAR.nc",
  "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20103352010365.L3b_MO_PAR.nc")

# This doesn't download the whole file...

for(url in par_list){
  browseURL(url)
  Sys.sleep(300)
}

## figure out which didn't download...
lists <- list.files(here("raw_data", "PAR"))

for(url in par_list){
  if(!file.exists(file.path("..", "macmod_processing", "raw_data", "PAR", basename(url)))){
    # print(url)
    browseURL(url)
    Sys.sleep(200)
  }
  else{
    next
  }
}

basename(par_list[3])

basename(lists[3])

```


```{r}
chl_files<- c("https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20050012005031.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20050322005059.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20050602005090.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20050912005120.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20051212005151.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20051522005181.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20051822005212.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20052132005243.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20052442005273.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20052742005304.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20053052005334.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20053352005365.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20060012006031.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20060322006059.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20060602006090.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20060912006120.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20061212006151.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20061522006181.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20061822006212.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20062132006243.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20062442006273.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20062742006304.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20063052006334.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20063352006365.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20070012007031.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20070322007059.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20070602007090.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20070912007120.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20071212007151.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20071522007181.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20071822007212.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20072132007243.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20072442007273.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20072742007304.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20073052007334.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20073352007365.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20080012008031.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20080322008060.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20080612008091.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20080922008121.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20081222008152.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20081532008182.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20081832008213.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20082142008244.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20082452008274.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20082752008305.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20083062008335.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20083362008366.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20090012009031.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20090322009059.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20090602009090.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20090912009120.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20091212009151.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20091522009181.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20091822009212.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20092132009243.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20092442009273.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20092742009304.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20093052009334.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20093352009365.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20100012010031.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20100322010059.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20100602010090.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20100912010120.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20101212010151.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20101522010181.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20101822010212.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20102132010243.L3b_MO_CHL.nc", "https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20102442010273.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20102742010304.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20103052010334.L3b_MO_CHL.nc",
"https://oceandata.sci.gsfc.nasa.gov/cgi/getfile/A20103352010365.L3b_MO_CHL.nc")

for(url in chl_files){
  browseURL(url)
  Sys.sleep(120)
}
    

for(url in chl_files){
  if(!file.exists(file.path("..", "macmod_processing", "raw_data", "Chl-A", basename(url)))){
    # print(url)
    browseURL(url)
    Sys.sleep(200)
  }
  else{
    next
  }
}
    
```    
    
Then, we can reconfigure, crop and mask thes, then resample them to a 5 degree grid.
```{r}
# First for chlorophyll...
chl_filenames <- list.files(here("raw_data", "Chl-A"), full.names = TRUE)

test <- nc_open(here("raw_data", "Chl-A", "A20050012005031.L3b_MO_CHL.nc"))

## UGH


resample_fx <- function(input_files){
  # Open the input file...
  ncin <- nc_open(input_files)
  # We keep DIN, DIC, SST
  var_list <- names(ncin$var[c(2,3,5)])
  # We'll make a brick (and crop) function that we can apply to each variable
  # Our dimensions are lat long, and time is the z dimension.
  brick_fx <- function(variable){
    brk <- brick(input_files, varname = variable)
    # Change the extent of the brick to lat/lon
    extent(brk) <- sabgom_extent
    # Crop to west florida:
    cropped <- crop(brk, wf_extent)
    # Save the file
    writeRaster(cropped, 
                filename = here("output",
                                paste0(tools::file_path_sans_ext(basename(input_files)),
                                      "_",
                                      variable,
                                      ".tif")
                                ),
                overwrite = TRUE)
  }
  # run our function for each variable...
  lapply(var_list, brick_fx)
}


```

# Wavewatch processing
```{r}
# Write a function to crop, and reasample the wavewatch data:

wavewatch_names <- list.files(here("scratch", "wavewatch"))

wavewatch_fx <- function(file){
  r <- raster(here("scratch", "wavewatch", file))
  r_crop <- crop(r, wf_extent)
  r_resample <- resample(r_crop, blank)
  name <- paste(basename(tools::file_path_sans_ext(file)), ".crop", ".tif", sep = "")
  writeRaster(r_resample, here("output", "wavewatch", name))
}

lapply(wavewatch_names, wavewatch_fx)
```

